Instructions for developing new pages for the MarineOmics webpage

### 2023-12-13 DRAFT_DNA_methylation.Rmd
Update DRAFT_DNA_methylation.Rmd
showing kathryn how pull requests work

>>>>

- Sequence quality assessment
- Read alignment
- Methylation quantification
- File conversions
- Potential downstream applications. Although this tutorial will not provide code for downstream applications such as differential methylation analysis, it will link to other open-access resources and examples.

## What to expect
DNA methylation at CpG locus can vary to 0-100%. Like wise methyation at the level Generally speaking in
